Mapping plant-pollinator interactions across Europe

### 2024-01-04 Manuscript/Ms.qmd
Minor edits on Ms

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr) #For handling fata 
library(ggplot2) #For plotting
library(giscoR) #For plotting
library(sf) #For handling coordinates and plotting
library(patchwork)#For plotting
library(ggstar) #For plotting (cool shapes)
library(scales) #For plotting (decimals on axes)
```

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Print number of countries
data = readRDS("../Data/Interactions_uncounted.rds")
#Country number
country_number = data %>% 
select(Country) %>% 
n_distinct()
#Study number
study_number = data %>% 
select(Study_id) %>% 
n_distinct()
#Minimum year
min_year = data %>% 
select(Year) %>% 
slice(which.min(Year)) %>% 
pull()
#Maximum year
max_year = data %>% 
select(Year) %>% 
slice(which.max(Year)) %>% 
pull()
#Number of interactions
interaction_number = nrow(data)
#Check number of accepted pollinators
pollinator_spp_number = data %>% 
select(Pollinator_rank, Pollinator_accepted_name)%>%
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name) %>% 
n_distinct()
#Check number of plant species
plant_spp_number = data %>% 
select(Plant_rank, Plant_status, 
Plant_matchtype, Plant_accepted_name) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name) %>% 
n_distinct()

@@

@@

This European metaweb consist of datasets of plant-pollinator interactions compiled initially by a wide number of researchers and institutions within the European continent. This dataset covers `r country_number` countries and consist of `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year`, and accounts for a total of `r prettyNum(interaction_number, big.mark=",")` interactions from `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species.

Shared species across studies (describe trend), added now in graph 1?

Update graph 1 (Add shared species of plants and pollinators?)

## Species coverage

@@

>>>>

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr) #For handling fata 
library(ggplot2) #For plotting
library(giscoR) #For plotting
library(sf) #For handling coordinates and plotting
library(patchwork)#For plotting
library(ggstar) #For plotting (cool shapes)
library(scales) #For plotting (decimals on axes)
library(lubridate) #To operate with dates
library(tidyr) #Reshape data (wide format)
library(stringr) #Fix/modify strings

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Print number of countries
data = readRDS("../Data/Interactions_uncounted.rds")
#Country number
country_number = data %>% 
select(Country) %>% 
n_distinct()
#Study number
study_number = data %>% 
select(Study_id) %>% 
n_distinct()
#Average study number
studies_by_country = data %>% 
group_by(Country) %>% 
summarise(study_number = n_distinct(Study_id)) %>% 
summarise(mean(study_number)) %>% 
pull()
#$\bar{x}_\frac{studies}{country}$ = `r studies_by_country`
#Sampling method
Sampling_method = data %>% 
group_by(Study_id) %>% 
distinct(Sampling_method) %>%  
ungroup() %>% 
count(Sampling_method) %>% 
mutate(percent_method = n/sum(n) *100) %>% 
mutate(Sampling_method = recode_factor(Sampling_method, "Transect" = "transects"))
#1st most common sampling methodology
most_common_method = Sampling_method %>% 
filter(percent_method == max(percent_method)) 
#Minimum year
min_year = data %>% 
select(Year) %>% 
slice(which.min(Year)) %>% 
pull()
#Maximum year
max_year = data %>% 
select(Year) %>% 
slice(which.max(Year)) %>% 
pull()
#Number of interactions
interaction_number = nrow(data)
#Check number of accepted pollinators
pollinator_spp_number = data %>% 
select(Pollinator_rank, Pollinator_accepted_name)%>%
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name) %>% 
n_distinct()
#Check number of plant species
plant_spp_number = data %>% 
select(Plant_rank, Plant_status, 
Plant_matchtype, Plant_accepted_name) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name) %>% 
n_distinct()
#Extract percentage of studies conducted during a single year
dates = data %>% 
select(Study_id, Network_id,Sampling_method, Day, Month, Year) %>% 
mutate(Date = dmy(paste(Day, Month, Year, sep = "-"))) %>% 
group_by(Study_id) %>% 
summarise(Count = n_distinct(Year))
#Filter studies with only one year
one_year = dates %>% 
filter(Count == 1) %>% 
pull() %>% 
length() / nrow(dates) * 100
#Obtain date information
dates = data %>% 
select(Study_id, Network_id,Sampling_method, Day, Month, Year) %>% 
mutate(Date = dmy(paste(Day, Month, Year, sep = "-")))

dates1 = dates %>% 
group_by(Study_id, Network_id, Sampling_method) %>% 
summarise(Min_date = min(Date), 
          Max_date= max(Date), 
          Sampling_days = n_distinct(Date)) %>% 
mutate(Sampling_period = as.numeric(Max_date - Min_date)) %>% 
mutate(Study_number = as.integer(str_extract(Study_id, "[^_]+")), 
       .before=Study_id) %>% 
arrange(Study_number) %>% 
mutate(Sampling_period = case_when(!is.na(Sampling_period) ~ Sampling_period + 1,
TRUE ~ NA)) %>% 
mutate(Sampling_days = case_when(!is.na(Sampling_period) ~ Sampling_days,
TRUE ~ NA))
#Extract min and max number of sampling days
min_sampling_day = dates1 %>% pull(Sampling_days) %>% min(na.rm = TRUE)
max_sampling_day = dates1 %>% pull(Sampling_days) %>% max(na.rm = TRUE)
#Extract average of sampling days across networks and studies
average_sampling_days = dates1 %>% 
ungroup() %>% 
group_by(Study_id) %>% 
summarise(mean_sampling_days = mean(Sampling_days, na.rm = TRUE)) %>% 
ungroup() %>% 
summarise(mean(mean_sampling_days, na.rm = TRUE)) %>% 
pull()
```

@@

This European metaweb consist of datasets of plant-pollinator interactions compiled initially by a wide number of researchers and institutions within the European continent. This dataset consist of `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` on `r country_number` different countries (**Figure 1a**). The dataset contains a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions, considering interaction as the contact of a given pollinator to the reproductive structure of a particular plant, from `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species. The majority of plant and pollinator species tend to be regionally specific, with only a minor portion of them being shared across a broad range of studies (**Figure 1b**). These different studies differ in sampling effort and methodology, although most studies took place within a single flowering season (`r format(round(one_year, 2), nsmall = 2)`%), sampled a given location an average of `r format(round(average_sampling_days, 2), nsmall=2)` days, and documented interactions mostly by using `r  most_common_method[[1]]` as sampling method (`r format(round(most_common_method[[3]], 2), nsmall = 2)`%).

## Taxonomic coverage

@@

Check presentation from Herrera for cool graphs summarising patterns
